Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-11-22 final/ms.tex
make a submission version

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
\usepackage{url}
%\usepackage{natbib}
%\usepackage{xspace}
\def\arcsec{$^{\prime\prime}$}
\bibliographystyle{apj}
\newcommand\degree{{^\circ}}
\newcommand\surfb{$\mathrm{mag}/\square$\arcsec}
\newcommand\Gyr{\rm{~Gyr}}
\newcommand\msun{\rm{M}_\odot}
\newcommand\kms{km s$^{-1}$}
\newcommand\al{$\alpha$}
\newcommand\ha{$\rm{H}\alpha$}
\newcommand\hb{$\rm{H}\beta$}
\newcommand\HI{\ion{H}{1}}

@@

\begin{abstract}
We present IFU observations of the giant low surface brightness galaxies Malin~2 and UGC~6614.  We fit the stellar dynamics of these systems and compare their spatially resolved spectra to star formation history models.  We argue that Malin~2 and UGC~6614 are normal elliptical galaxies which have undergone high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.  We find the stellar dynamics are consistent with earlier measurements of the GLSB \HI\ disks.  The stellar populations of the GLSB disks are dominated by old metal-poor stars, while the central ellipticals are metal rich.

@@

Observers tend to classify GLSB systems as normal spirals.  \citet{Matthews01b} list Malin~2 as an Scd while \citet{Das13} concludes that GLSB systems are an extreme form of late type spiral galaxies.  Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.  Even the Galaxy Zoo project \citep{Willett13}  classifies GLSB galaxies as spirals.  While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest typical spirals \citep{Dalcanton97}.

The disks in GLSB systems are incredibly large, with Malin~1 being detected in $R$-band to a radius of over 100 kpc \citep{Moore06}.  Disks of this size are a challenge for typical $\Lambda$CDM cosmology galaxy formation and exotic formation scenarios have been proposed for GLSB systems.  \citet{Mapelli08} form GLSB-like galaxies in simulations via the fading of collisional ring galaxies.  In their model, a collision sets off an expanding ring of star formation.  As the star formation subsides and the stellar population ages, the ring galaxy fades over $\sim$100 Myr to resembles observed GLSBs.  One obvious problem with this scenario is that most GLSB's are relatively isolated, and thus there are no obvious candidates for the impactor systems that would have triggered the star formation burst.

@@

%These distances have occasionally been reached by x-ray observations of giant elliptical galaxies \citep{Buote12}.

%In this paper, we use IFU spectroscopy to measure the star formation histories of two GLSB systems.

%The problem with considering GLSB systems as normal spirals is that they are clearly outliers when one considers the specific angular momentum of the systems.  The difference between high surface brightness (HSB) spirals and low surface brightness spirals (LSB), could simply be an issue of specific angular momentum. -this goes in the discussion I think. \citet{Dutton12} is a nice paper on how disk galaxies get their angular momentum--I'll need to make a calc of how much J is in the GLSB disks to compare it.

%\citet{Raskutti14} use VIRUS-P to look at stellar halo kinematics of massive ellipticals.  Lots of good stuff on fast/slow rotators.  Also a very nice plot showing the radial gradients in age and metallicity as measured from Lick indices.  They don't see any sharp transition like I do, all very smooth age and metal curves.

@@

In \S\ref{sec:obs} we present new observations of Malin~2 and UGC~6614. In \S\ref{sec:compare_gals}, we compare the general properties of GLSB galaxies to sample of galaxies drawn from SDSS and the THINGS survey.  In \S\ref{sec:kinematics} and \S\ref{sec:sfh} we measure the stellar kinematics and star formation histories from our spectra. In \S\ref{sec:discussion}, we discuss what our observations imply for the possible formation mechanisms for GLSB systems.

%\citet{Pickering97} has the \HI\ rotation curves of these guys.  For UGC~6614, has M \HI\ $= 2.5 \pm0.2\times 10^{10} \msun h_{75}^{-2}$.  And $3.6 \pm 0.4 \times 10^{10} \msun h_{75}^{-2}$for Malin~2.  Notes that these are galaxies that are massive and DM dominated.  In Malin~2, they find some gas moving relative to the regular rotating disk, and suspect that a dwarf fell though and stimulated star formation and this could be how stars managed to form in the low density environment.

%Can we say that the stars formed in a higher density environment and then got dispersed.

%\citet{Das13} look at the environments of GLSB systems.  He says that GLSBs are an extreme form of late type spiral galaxies.  I think I can show that no, they are really normal elliptical galaxies that happen to have accreted disks.

%Nice paper on galaxies that live in voids and how one did manage to build a polar \HI\ disk with no stars: \citet{Stanonik09}

%Chemical abundances in a polar disk:  \citet{Spavone10}

%a near scoop by \citet{Lelli10}.  They re-analyze \HI\ data on Malin 1 and one other.  But a nice place to look for introduction material.  They point out that GLSB galaxies might be normal HSB galaxies in the center.  They claim to see steeply rising rotation curves, and compare to formation mechanisms.

%\citet{Morganti97} look at an elliptical with an \HI\ disk.  Find a nice flat rotation curve.
%\citet{Emonts08}  Another massive \HI\ ring around an S0 galaxy.
%\citet{Weijmans08} another \HI\ ring around an early type.  Anne-Marie has lots of SAURON papers pushing out to large radii in ellipticals.

%\citet{Ibata05} look at extended disk of M31.
%\citet{Ibata13} claim M31 satellites are co-planer.  
%\citet{McConnachie09} M31 survey showing lots of merger structure.

%Bothun of course has a nice web page with images at:  http://zebu.uoregon.edu/sb2.html
%another nice image at http://www.capella-observatory.com/ImageHTMLs/Galaxies/UGC6614.htm

%From \citet{Matthews01b}, \HI\ measurements on the gals:
%name          rms   Fmax W20   W50   HRV  e_HRV S\HI\  eS\HI\  S/N
%F 568-6    *  2.29  17.5 420   393   13829  7  4.20  0.64  7.6 
%UGC~6614   *  2.86  81.2 290   255    6351  2 15.94  0.72 28.4 
%\citet{Matthews01b} also lists some incs values--calls Malin2 an Scd/Sd galaxy, has some good tables that are only available on-line.  I'll need to compare my stellar kinematics to the \HI\ kinematics.

%\cite{Rahman2007} has Spitzer observations of a few GLSB galaxies.

%\citet{Das10} find CO in Malin~2.  Make some points about it being stable

%\citet{Mapelli12} making ring galaxies from off center collisions.  
%\citet{Mapelli08} look at if ring galaxies could evolve into GLSB systems.

%\citet{Schiminovich13}:  Observe \HI\ shells in ellipticals.  
%\citet{Iodice06}:  Nice minor and major axis observation of a polar-ring galaxy.  
%\citet{Brook08b}:  Makes a polar ring galaxy via extended accretion of cosmological gas.  They say polar disk galaxies are built just like the outskirts of regular galaxies, they just happen to be very mis-aligned.

%\citet{Schweizer89} Do a similar study with IC 2006, where they observe an \HI\ ring around the elliptical galaxy to get the total mass at large radii.  Looks like they get out to about 12.5 kpc.

%\citet{Oosterloo07} HIPASS detection of \HI\ gas around 30 early-type galaxies.  Most have regular disk or ring kinematics.  Suggest these are ancient.  They don't seem to have the resolution to do in-depth kinematics and DM halo stuff.

%\citet{Magain13} look at strong lenses around 25 ellipticals, and then claim they see no evidence for extended DM halos.  Confusing plot--Maybe they get out to 5 $R_{1/2}$?  They say they only need a factor of 2, that could come from baryonic dark matter.

%\citet{Spray95} CCD imaging of 8 GLSB systems.

%\citet{Morganti13} Do modeling of ellipticals with declining velocity dispersion profiles.  Good place to start looking for the best way to model the long-slit data.

%\citet{Buote12} review of dark matter in ellipticals from x-ray observations.

%-need to look up some Thilker papers on extended UV disks, since these objects could be similar.  From his talk, UGC 1382 shows up in stripe 82 coadd (and NUV).  UGC 3642, GALEX shows a disk, and \HI\ is counter rotating.

%\citet{Salim10} Looks at HST imaging of z = 0.1 early type galaxies that have UV excess, and finds some extended disks.  They think the gas and star formation is coming from minor mergers or accretion.

%\citet{Salim12} Finds 2 more GLSB type objects -- could be a sign that there are multiple routes to making GLSB systems.

\begin{deluxetable*}{l l c c c c c c}
%\tabletypesize{\small \footnotesize \scriptsize}
\tabletypesize{\small}
%\rotate
\tablewidth{0pt}
%\tablenum{num}
%\tablecolumns{num}
%\tableheadfrac{num}
\tablecaption{Basic Properties of GLSB Galaxies}
\tablehead{
\colhead{Name} & \colhead{SDSS ID}   &  \colhead{z}  &\colhead{$r$}  & \colhead{$R_e$} 
& \colhead{$\sigma$}  & \colhead{\HI\ Mass} & \colhead{Stellar Mass} \\
     &  \colhead{(DR 10)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms} & \colhead{log$_{10}$M$_{\odot}$} & \colhead{log$_{10}$M$_{\odot}$}
\label{basic_prop}}    
\startdata
Malin 1 & 1237661068728139925 & 0.083 & 16.70 & 1.86 & 177 &  10.9 & 11.1 \\
Malin~2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 &  10.5 & 10.9
\enddata
\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
\end{deluxetable*}

% SDSS stellar masses.  using stellarMassFSPSGranEarlyDust:
% Malin~2:  logMass	11.3307373297902
% Malin 1:  logMass	11.1328074307929
% UGC~6614: logMass	10.8745260407613

% Updating the Pickering MI masses:
% M_\HI\ = 2.36e5 * D^2 * int(S)
% D = c(z+0.5(1.0-q_0)z^2)/H_0
% int(S) = 4.4 Jy km/s for Malin~2
%        = 15.0 for UGC~6614
% cosmolopy using h = 0.704.  
% cosmolopy says D_L = 202.9 and 90.9 Mpc
% so that gives me M_\HI\'s of 4.27e10 and 2.92e10

%  using scales of 0.940 and 0.444 kpc/arcsec.

@@

%The other way to measure the dark matter halo of an elliptical is to use gravitational lensing.  \citet{Belokurov07} find a large ring in SDSS.

%list of more lense papers here: http://www.galaxyzooforum.org/index.php?topic=275811.0

@@

%dates:  Feb 19, 20, 2010.  March 18-21, 2010.  April 6-8, 2010.

@@

% Let's punt the APO spectra to the next paper--I don't think it adds much to this one anyway.
%\subsection{Longslit spectra}

%Observations were made using the Dual Imaging Spectrograph (DIS) on
%the ARC 3.5 meter telescope at Apache Point Observatory (APO).  Malin~2 was observed on 4/01/13, and UGC 06614 was observed 5/01/13.  Both galaxies were observed with the  gratings and multiple positions of the 1.5\arcsec\ slit.
%-insert table with galaxy name, position, total exposure time
%-insert figure showing slit positions overlayed on the SDSS thumbnails.

@@

By eye, GLSB systems resemble large faint spiral disks at large radii, and regular ellipticals at their centers.  In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1 and 2 and UGC~6614.  In this section, we compare the properties of the GLSB centers and disks with other systems.

@@

% based on WMAP7+BAO+H0 mean
%>>> fidcosmo
%{'tau': 0.087, 'omega_n_0': 0.0, 'sigma_8': 0.809, 'h': 0.704, 'N_nu': 0, 'omega_lambda_0': 0.7274, 'n': 0.963, 'Y_He': 0.24, 'z_reion': 10.4, 'omega_b_0': 0.0456, 'omega_k_0': 0.0, 't_0': 13.75, 'omega_M_0': 0.2726}

@@

\begin{figure*}
\epsscale{.4}
\plotone{Plots/Color_Magnitu_Diagram.eps}\plotone{Plots/Faber_Jackson_Relation.eps}\\
\plotone{Plots/Fundamental_Plane.eps}\plotone{Plots/mg_sigma.eps}
\epsscale{1}
\caption{
Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin~2 and UGC~6614.  Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.  Left:  The $r$-band fundamental plane from SDSS along with our GLSB galaxies and best-fit line.  Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.   From the point of view of the SDSS data reduction pipeline, GLSB galaxies appear as relatively normal red elliptical galaxies.  \label{elliptical_relations}}
\end{figure*}

@@

%For comparison, \citet{Williams13} trace star formation out to 11 disk scale lengths (radius of 22 kpc) in NGC 2403.

%Papers that have large \HI\ rotation curves that I might compare to:
%\citet{DeBlok2008,Swaters09,Verheijen01}

@@

% /Users/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure*}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, GLSB \HI\ data from Malin 1 from \citet{Pickering97} and GLSB stellar radii from \citet{Galaz15}, \citet{Kasparova14}, and this paper.  Here, $R_{max}$ is the maximum radius with an \HI\ or optical detection.  For the GLSB galaxies, the circular points show the maximum \HI\ detection radius and stars-shaped points show the maximum detected stellar light radius.  All points are maximum detection radii, and thus should be considered lower limits.   \label{disk_comp}}
\end{figure*}

@@

%It would be nice to be able to use just the OII doublet to measure gas velocities from some of the galaxies.  Paper that discusses the range of OII ratio values in \citet{Wang04}.  Looks like it's usually around 0.5, but in low density regions it goes to 1.4.  Fuck.

@@

%using /astro/store/shared-scratch1/yoachim/Research/GLSB/Analysis/mass_estm.pro
If we use the circular speed of the \HI\ data from the literature, we end up with dynamical masses of $25\times 10^{11} \msun$ for Malin~2 and $6.5\times 10^{11} \msun$ for UGC~6614 (dynamical to stellar mass ratios of 18 and 14 respectively).   %Looks like they both have M$_{\rm{HI}}$ around 3-4 $10^{10} \msun$.

%$R_e = 7.3$\arcsec for UGC06614\\
%$R_e = 7.17$\arcsec for Malin2

%-crap, whatever happened to the gas kinematics?  There are emission lines out there--are they bright enough to get in single fibers of not?  Looks like for Malin~2 the emission lines are only coming from one side of the galaxy.  UGC~6614 is mostly emission from the center.

%print, rcmass(42.,280.)
%print, rcmass(17.,200.)

%scales=[0.940, 0.444] ;kpc/arcsec.  CMB frame from NED
%re = [7.17, 7.3] ;effective radii in arcsec

%-It would be great to get high resolution \HI\ observations of these systems since they could probably be higher spatial resolution.

@@

Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the best fitting single model.  We break the star formation history into three age bins, 0-10 Gyr, 10-11.5 Gyr, and 11.5-12 Gyr.  We assume each age bin has a constant star formation with a level of 0, 0.5, 1, or 10 solar-masses per year.  Each SFH can have a metallicity of [Z/H] = -2.3, -1.70, -0.70, -0.40, 0.0, or 0.40.  We do not include any metallicity evolution, as all the age bins in a given model have the same metallicity.  This gives us 361 unique non-zero model spectra. We use \citet{Bruzual03} with a Chabrier IMF to generate the model spectra.

Figures~\ref{malin2_binmap} and~\ref{ugc_binmap} show the fibers that were binned and the resulting spectra for Malin~2 and UGC 06614.  Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.  We find the best-fitting single model spectrum for each observed binned spectrum. When fitting, we include a low order multiplicative polynomial to match any dust extinction or flux calibration errors in the observations.  This means our fits are for the relative star formation histories, but not the absolute star formation rates (e.g., a model constant star formation history of 1 M$_\sun$ yr$^{-1}$ is an equally good fit as 10 M$_\sun$ yr$^{-1}$.)

@@

A problem with fitting observed galaxy spectra with templates is that residuals between the model and data are dominated by non-Gaussian systematic effects such as template mis-match and improper parameterization of the SFH.  Since the residuals are non-Gaussian, there is no statistical formalism for generating uncertainties in the fit.  To generate our error bars, we look at the range of fits which have $\chi^2$ values within 100 of the minimum.  In many cases, this eliminates nearly all fits except for the minimum.  In these cases, we use the 4 best-fitting models to estimate the range of possible fits.

@@

%\section{Disk Progenitors}

%It should be relatively easy to speculate about the galaxies that merged to form the disk. I can pull \HI\ masses, and then calc some stellar masses given the SDSS photometry and my own stellar M/L ratios.  Then given a baryonic mass and a typical stellar metallicity, it should be easy match that up to something.  Using baryonic TF relation, I'm getting pretty large $V_c$ values for what the accreted galaxy would have been.  I guess we could even speculate that this was a 3+ body encounter, so multiple gas rich systems that settle in.  That would help explain the low metallicities.

%Figure~\ref{thingsMHI} shows the total \HI\ mass for galaxies observed in the THINGS survey \citep{Walter2008}, along with the \HI\ masses for GLSB galaxies \citep{Pickering97}.

%We can't really use the stellar luminosity of the disk to constrain the progenitor since there are signs of current {\emph in situ} star formation in the disks.  However, the very low stellar metallicities point to low-mass progenitors.

%Hard to estimate what the progenitor system of the disks were.  Is there a good plot of disk \HI\ mass and metallicity out there?  Might even need to measure Lick indices to try and get everything on the same metallicity system.

%These systems are rare enough, that one might imagine rather complicated scenarios for creating them.  For example, a three-body encounter could eject one galaxy while leaving a second in a nearly circular orbit.  Back of the envelope, a galaxy ejected at 5000 \kms would go 1.5 degrees per gigayear.  Even if the ejection was partly along the line of sight, it would be hard to find several gigayears later.  Unlike the collisional ring scenario where one would expect the galaxy that stimulated the ring formation to still be nearby.

@@

%--now on new mac.  /Users/yoachim/Research/GLSB/THINGS/guess_projen.py
\begin{figure*}
\epsscale{0.5}
\plotone{Plots/things_projenguess.eps}
\epsscale{1}
\caption{Comparison of GLSB \HI\ masses \citep{Pickering97} with \HI\ masses measured in the THINGS survey \citep{Walter2008}.  While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a V$_{\rm{max}}\sim$110 km/s or smaller galaxy, assuming the merger did not trigger large amounts of star formation and feedback. \label{thingsMHI}}
\end{figure*}

@@

One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figures~\ref{metal_malin2} and~\ref{metal_ugc}).  For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.  This is a very sharp gradient compared to what has been found in normal spirals for the bulge-to-disk transition region.  \citet{MacArthur09} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.  Using broadband colors, \citet{MacArthur04} also found metallicity gradients were generally very shallow, with steep metallicity gradients only in very late-type spiral galaxies. Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid (i.e., they could have metallicities greater than [Z/H]=0.7). We have also spatially binned data, possibly washing out how sharp the transition is between bulge and disk.

\citet{Sanchez14} measure the Oxygen abundance from gas emission lines in a large sample of spiral galaxies and find a characteristic slope of $\alpha_{\rm{O/H}} = -0.1$\ dex $r_e^{-1}$ between 0.3 and 2 effective radii.  The metallicity gradients we observe in Malin~2 and UGC~6614 are factors of 2-4 steeper than the typical spiral. Also, of the 193 galaxies in \citet{Sanchez14} only four have a slope steeper than -0.3 \ dex $r_e^{-1}$ \citep[Figure~6]{Sanchez14}.  In their Figure~9, they combine the data to show a typical gas metallicity curve that drops linearly until $r_e\sim2$ and then flattens to a constant value.  This shape is very different from the step function change we observe in the GLSBs.

These are incredibly steep metallicity gradients.  The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin~2 and $\sim -0.68$ for UGC~6614.  These are very steep compared to gradients typically observed in elliptical galaxies \citep{Greene12, Greene15}.  Other cites for elliptical gradients \citep{Kuntschner10}

\citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallicity gradients for late type galaxies.

% Malin~2: R_e = 7.17"
% UGC : 7.3"

\citet{Kasparova14} present one of the most in depth observational studies of Malin~2.  Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc.  \citet{Kasparova14} also measure gas metallicities and find the metallicity drops from solar in the center of the system to half-solar at $r=30$\ kpc.  It is probably foolish to directly compare gas and stellar metallicities, but it is interesting that the gas metallicity gradient appears to be much lower than the stellar gradient.  This is probably consistent with a low metallicity gas-rich galaxy merging with an elliptical system that has much higher stellar metallicity, although a detailed simulation would be helpful in confirming what the final expected gas metallicity gradient should be.

@@

%Based on observations obtained with the Apache Point Observatory
%3.5-meter telescope, which is owned and operated by the Astrophysical
%Research Consortium.

@@

%\bibliography{/astro/users/yoachim/Dropbox/Papers/Bib_files/big_jabref}
%\bibliography{/Users/yoachim/Dropbox/Papers/Bib_files/big_jabref.bib}
\bibliography{big_jabref.bib}

>>>>

\documentclass[12pt,preprint]{aastex}
%\documentclass{emulateapj}
\usepackage{url}
%\usepackage{natbib}
%\usepackage{xspace}
\def\arcsec{$^{\prime\prime}$}
\bibliographystyle{apj}
\newcommand\degree{{^\circ}}
\newcommand\surfb{$\mathrm{mag}/\square$\arcsec}
\newcommand\Gyr{\rm{~Gyr}}
\newcommand\msun{\rm{M}_\odot}
\newcommand\kms{km s$^{-1}$}
\newcommand\al{$\alpha$}
\newcommand\ha{$\rm{H}\alpha$}
\newcommand\hb{$\rm{H}\beta$}
\newcommand\HI{\ion{H}{1}}

@@

\begin{abstract}
We present IFU observations of the giant low surface brightness galaxies Malin~2 and UGC~6614.  We fit the stellar dynamics of these systems and compare their spatially resolved spectra to star formation history models.  We argue that Malin~2 and UGC~6614 are normal elliptical galaxies that have undergone high angular momentum mergers which formed their GLSB disks, making them unique systems for probing the dark matter halos of elliptical systems.  We find the stellar dynamics are consistent with earlier measurements of the GLSB \HI\ disks.  The stellar populations of the GLSB disks are dominated by old metal-poor stars, while the central ellipticals are metal rich.

@@

Observers tend to classify GLSB systems as normal spirals.  \citet{Matthews01b} list Malin~2 as an Scd while \citet{Das13} conclude that GLSB systems are an extreme form of late type spiral galaxies.  Similarly, \citet{Kasparova14} claim that the large dark matter scale of Malin~2 can explain it's features.  Even the Galaxy Zoo project \citep{Willett13}  classifies GLSB galaxies as spirals.  While GLSB systems superficially resemble normal spiral galaxies, they are clearly extreme outliers when their scale lengths are compared to other galaxy samples, being around a factor of 2 larger than the largest normal spirals \citep[Figure~4]{Dalcanton97}.

The disks in GLSB systems are incredibly large, with Malin~1 being detected in $R$-band to a radius of over 100 kpc \citep{Moore06}.  Disks of this size are a challenge for typical $\Lambda$CDM cosmology galaxy formation theories and more exotic formation scenarios have been proposed for GLSB systems.  \citet{Mapelli08} form GLSB-like galaxies in simulations via the fading of collisional ring galaxies.  In their model, a collision sets off an expanding ring of star formation.  As the star formation subsides and the stellar population ages, the ring galaxy fades over $\sim$100 Myr to resembles observed GLSBs.  One obvious problem with this scenario is that most GLSB's are relatively isolated, and thus there are no obvious candidates for the impactor systems that would have triggered the star formation burst.

@@

@@

In \S\ref{sec:obs} we present new observations of Malin~2 and UGC~6614. In \S\ref{sec:compare_gals}, we compare the general properties of GLSB galaxies to samples of galaxies drawn from the Sloan Digital Sky Survey (SDSS) and  The \HI Nearby Galaxy Survey (THINGS).  In \S\ref{sec:kinematics} and \S\ref{sec:sfh} we measure the stellar kinematics and star formation histories from our spectra. In \S\ref{sec:discussion}, we discuss what our observations imply for the possible formation mechanisms for GLSB systems.

\begin{deluxetable}{l l c c c c c c}
%\tabletypesize{\small \footnotesize \scriptsize}
\tabletypesize{\small}
%\rotate
\tablewidth{0pt}
%\tablenum{num}
%\tablecolumns{num}
%\tableheadfrac{num}
\tablecaption{Basic Properties of GLSB Galaxies}
\tablehead{
\colhead{Name} & \colhead{SDSS ID}   &  \colhead{z}  &\colhead{$r$}  & \colhead{$R_e$} 
& \colhead{$\sigma$}  & \colhead{\HI\ Mass} & \colhead{Stellar Mass} \\
     &  \colhead{(DR 10)}   &     &  \colhead{(mag)}    & \colhead{arcsec} & \colhead{\kms} & \colhead{log$_{10}$M$_{\odot}$} & \colhead{log$_{10}$M$_{\odot}$}
\label{basic_prop}}    
\startdata
Malin 1 & 1237661068728139925 & 0.083 & 16.70 & 1.86 & 177 &  10.9 & 11.1 \\
Malin~2 & 1237667735572381852 &   0.046 & 14.34 & 7.17 & 202  &  10.6 & 11.3 \\
UGC 06614 & 1237668585435365393 &  0.021 & 13.52 & 7.3 & 150 &  10.5 & 10.9
\enddata
\tablecomments{\HI\ masses updated to our adopted cosmological parameters from \citet{Pickering97}.  The rest taken from SDSS. Stellar masses calculated from \citet{Conroy09}}
\end{deluxetable}

@@

@@

@@

@@

By eye, GLSB systems resemble large faint spiral disks at large radii, and regular ellipticals at their centers.  In the Sloan Digital Sky Survey Data Release 10 (SDSS DR10) \citep{Ahn14}, the Galaxy Zoo classifications \citep{Willett13} are spiral for Malin 1, Malin 2, and UGC~6614.  In this section, we compare the properties of the GLSB centers and disks with other systems.

@@

@@

\begin{figure*}
\epsscale{.4}
\plotone{Color_Magnitu_Diagram.eps}\plotone{Faber_Jackson_Relation.eps}\\
\plotone{Fundamental_Plane.eps}\plotone{mg_sigma.eps}
\epsscale{1}
\caption{
Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin~2 and UGC~6614.  Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.  Left:  The $r$-band fundamental plane from SDSS along with our GLSB galaxies and best-fit line.  Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.   From the point of view of the SDSS data reduction pipeline, GLSB galaxies appear as relatively normal red elliptical galaxies.  \label{elliptical_relations}}
\end{figure*}

@@

@@

\begin{figure*}
\epsscale{.5}
\plotone{things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, GLSB \HI\ data from Malin 1 from \citet{Pickering97} and GLSB stellar radii from \citet{Galaz15}, \citet{Kasparova14}, and this paper.  Here, $R_{max}$ is the maximum radius with an \HI\ or optical detection.  For the GLSB galaxies, the circular points show the maximum \HI\ detection radius and stars-shaped points show the maximum detected stellar light radius.  All points are maximum detection radii, and thus should be considered lower limits.   \label{disk_comp}}
\end{figure*}

@@

@@

If we use the circular speed of the \HI\ data from the literature, we end up with dynamical masses of $25\times 10^{11} \msun$ for Malin~2 and $6.5\times 10^{11} \msun$ for UGC~6614 (dynamical to stellar mass ratios of 18 and 14 respectively).

@@

Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the single best fitting model.  We break the star formation history into three age bins, 0-10 Gyr, 10-11.5 Gyr, and 11.5-12 Gyr.  We assume each age bin has a constant star formation with a level of 0, 0.5, 1, or 10 solar-masses per year.  Each SFH can have a metallicity of [Z/H] = -2.3, -1.70, -0.70, -0.40, 0.0, or 0.40.  We do not include any metallicity evolution, as all the age bins in a given model have the same metallicity.  This gives us 361 unique non-zero model spectra. We use \citet{Bruzual03} with a Chabrier IMF to generate the model spectra.

Figures~\ref{malin2_binmap} and~\ref{ugc_binmap} show the fibers that were binned and the resulting spectra for Malin~2 and UGC 06614.  Both galaxies have elliptical-galaxy like spectra in their centers, with outskirts that have significant emission lines.  We find the best-fitting single model spectrum for each observed binned spectrum. When fitting, we include a low order multiplicative polynomial to match any dust extinction or flux calibration errors in the observations.  This means our fits are for the relative star formation histories, but not the absolute star formation rates (e.g., a model constant star formation history of 1 M$_\sun$ yr$^{-1}$ is an equally good fit as a constant 10 M$_\sun$ yr$^{-1}$.)

@@

A problem with fitting observed galaxy spectra with templates is that residuals between the model and data are dominated by non-Gaussian systematic effects such as template mis-match and improper parameterization of the SFH.  Since the residuals are non-Gaussian, there is no statistical formalism for generating uncertainties in the fit.  To generate our error bars, we look at the range of fits which have $\chi^2$ values within 100 of the minimum.  In many cases, this eliminates nearly all fits except for the minimum.  In these cases, we use the 4 best-fitting models to estimate the range of possible parameters.

@@

@@

\begin{figure*}
\epsscale{0.5}
\plotone{things_projenguess.eps}
\epsscale{1}
\caption{Comparison of GLSB \HI\ masses \citep{Pickering97} with \HI\ masses measured in the THINGS survey \citep{Walter2008}.  While the \HI\ masses in the GLSB systems are high, they are consistent with what would be available in a merger with a V$_{\rm{max}}\sim$110 km/s or smaller galaxy, assuming the merger did not trigger large amounts of star formation and feedback. \label{thingsMHI}}
\end{figure*}

@@

One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figures~\ref{metal_malin2} and~\ref{metal_ugc}).  For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.  This is a very sharp gradient compared to what has been found in normal spirals for the bulge-to-disk transition region.  \citet{MacArthur09} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.  Using broadband colors, \citet{MacArthur04} also found metallicity gradients were generally very shallow, with steep metallicity gradients only in very late-type spiral galaxies. Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid (i.e., they could have metallicities greater than [Z/H]=0.7). We have also spatially binned data, possibly diluting how sharp the transition is between bulge and disk.

\citet{Sanchez14} measure the Oxygen abundance from gas emission lines in a large sample of spiral galaxies and find a characteristic slope of $\alpha_{\rm{O/H}} = -0.1$\ dex $r_e^{-1}$ between 0.3 and 2 effective radii.  The metallicity gradients we observe in Malin~2 and UGC~6614 are factors of 2-4 steeper than the typical spiral. Also, of the 193 galaxies in \citet{Sanchez14} only four have a slope steeper than -0.3 \ dex $r_e^{-1}$ \citep[Figure~6]{Sanchez14}.  In their Figure~9, they combine the data to show a typical gas metallicity curve that drops linearly until $r_e\sim2$ and then flattens to a constant value.  This shape is very different from the step function change we observe in GLSBs.

These are incredibly steep metallicity gradients.  The logarithmic gradients $\delta \rm{[Z/H]}\ \log{R/R_e}$ is $\sim -1.6$ for Malin~2 and $\sim -0.68$ for UGC~6614.  These are very steep compared to gradients typically observed in elliptical galaxies \citep{Kuntschner10, Greene12, Greene15}.  \citet{Wilkinson15} find -0.15 dex/$R_e$ gradients for early type galaxies and flat metallicity gradients for late type galaxies.

\citet{Kasparova14} present one of the most in depth observational studies of Malin~2.  Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc best fits the dynamics.  \citet{Kasparova14} also measure gas metallicities and find the metallicity drops from solar in the center of the system to half-solar at $r=30$\ kpc.  It is probably foolish to directly compare gas and stellar metallicities, but it is interesting that the gas metallicity gradient appears to be much lower than the stellar gradient.  This is probably consistent with a low metallicity gas-rich galaxy merging with an elliptical system that has much higher stellar metallicity, although a detailed simulation would be helpful in confirming what the final expected gas metallicity gradient should be.

@@

@@

\bibliography{ms}

\begin{figure}
\plottwo{sdssbinned_Malin2.eps}{Malin2mu.eps}
\epsscale{.5}
\plotone{Malin2profile_fit.eps}
\epsscale{1}
\caption{Upper Left:  SDSS image of Malin~2.  Upper Right:  Image made with the VIRUS-P datacube synthetic fiber magnitudes.  Lower:  An exponential fit to the fiber magnitudes.  Red points show fibers that were clipped while the solid line shows the best-fit.  \label{Malin2_fibers} }
\end{figure}
